\section{Portrait of a Graduate}

\textsc{An Indian Springs School graduate, having completed the course of study in Arts, will} $\ldots$ 

\begin{itemize}
  \item Demonstrate a command of content specific to their media of study. 
\item Demonstrate an appreciation for the acquisition of new content, knowledge, skills, and understanding, and be able to apply a methodical approach to acquire such.
\item Demonstrate an understanding of various efficient practice/rehearsal techniques.
\item Demonstrate practical studio safety, time-management, and self-discipline skills.
\item Understand the process of audition, rehearsal, and performance.
\item See the value in a positive studio and rehearsal environment, and understand how to make positive contributions
\item Understand, demonstrate, and appreciate the skill of communication in all forums.
\item Realize the value of the arts in the formation and communication of ideas.
\item Understand the need for collaboration and mutual respect in ensemble projects.
\item Recognize the value of empathy in collaborative and performative activities.
\item Value perseverance and follow-through in individual and group activities.
\item Develop appreciation of positive leadership skills in their particular artistic medium.
\item Acquire an inner compulsion to express themselves in a creative, not imitative, form.
\item Develop a healthy appreciation of self, peer, and professional critiques and reviews.
\item Value/respect their own perspective and aesthetic and learn to value/respect the perspective and aesthetic of others.
\item Understand and possess visual/musical/drama literacy, allowing them to effectively navigate the contemporary experience. 
\item Think critically about theatrical, visual, and aural information when it is presented and will be conscious of their theatric, visual, and aural culture output.
\item Self reflect/empathize/identify with or draw personal contrast with historical voices, styles and periods.
\item Develop an intellectual understanding of art concepts and a vocabulary to describe, analyze, compare, and judge works of art in various media and traditions.
\item Become critically-thinking, motivated, disciplined, passionate, ethical, respectful, empathetic and courageous young artists prepared for a global society.

\end{itemize}