\section{The Program}
Springs is  excited and proud to be a member of the Malone Schools Online Network (\href{https://maloneschoolsonline.org/}{MSON}) and is the only member school in the state of Alabama.  Per their FAQ\footnote{\href{https://maloneschoolsonline.org/faq/}{Source}}

\begin{quote}
  The Malone Schools Online Network (MSON) expands academic opportunities for motivated, upper-level students by connecting them with inspiring teachers and peers across the country in real-time online seminars. MSON courses provide challenge beyond the standard curriculum while nurturing students’ intellectual curiosity, building their independence and time management skills, and fostering relationships across geographical divides. Beyond its classes, MSON draws on its vibrant community to help teachers and school leaders collaborate and innovate in their schools, charting new territory in learning.
\end{quote}

\noindent \textbf{Malone School Online Networks Course Policies}


Note that MSON online courses meet at a fixed time, typically twice per week.  Because they do not fit into our rotating schedule, students will regularly miss their scheduled classes while attending their MSON course. 

\begin{enumerate}\itemsep=0mm
\item You must be a junior or senior to enroll.
\item The average from your core courses (English, History, Science, Math, Languages) from the “Quarter 3 - Report” must be at least 90.
\item You must have a good attendance record. 
\item The MSON course cannot be taken in place of an identical, or almost identical, course offered by the school, assuming the school course can be made to fit into your schedule. 
\item The course must be your 6th class (not counting PE in 11th grade). 
\item The course must be taken for credit. 
\item You must comply with the advertised add/drop dates, course prerequisites and the attendance and homework policies of the MSON instructor. 
\item You are responsible for catching up work that you miss from a Springs course because of your attendance at an MSON course.  \emph{This includes notifying your teacher at Springs ahead of every missed class.}  
\item Per MSON policy, their courses must be prioritized over all other courses/obligations.  This means you may have classes during a school break/holidays, other classes, choir, sports, and so on.  
\end{enumerate}

The MSON enrollment form can be found in Appendix 12.4.4

