\section{Portrait of a Graduate}

\textsc{An Indian Springs School graduate, having completed the course of study in Mathematics, will} $\ldots$ 

\begin{itemize}
  \item Perform elementary calculations and apply mathematical processes comfortably.
\item Need to understand the whys and hows of mathematics.
\item Communicate efficiently, accurately, and clearly in writing and speech.
\item Form logical, coherent arguments and judge the validity of others’ arguments.
\item Apply concepts and techniques from elementary mathematics to the world around them.
\item Use prior understandings to inform and strengthen new concepts.
\item Understand the importance of initial steps, that failure is a part of learning, and that growth is afforded by persistence.
\item Appreciate the ubiquity of mathematics in the world around them.
\item Guide personal decisions by specifying assumptions/non-negotiables and then make inferences based on these.
\item Apply mathematics to the sciences to form inferences and support the Scientific Method.
\item Apply the language of mathematics to the sciences to form inferences and support the Scientific Method.
\item Connect the numerical, algebraic, graphical, and verbal perspectives of mathematics.
\item Determine the appropriate structure or mathematical model so that one may
\begin{itemize}
\item Apply knowledge and skills to ...
\item Solve known and novel problems and ...
\item Interpret the results or outcomes from the structure or model
\end{itemize}
\item Collaborate and employ team-based approaches to explore concepts and solve problems.
\item Use the appropriate technological tool for the problem at hand.
\item Use statistics to become an educated citizen of our modern, data-driven world.

\end{itemize}