\section{Portrait of a Graduate}

\textsc{An Indian Springs School graduate, having completed the course of study in Science, will} $\ldots$ 

\begin{itemize}
  \item Engage in scientific questioning  to extend thinking and guide research.
\item Utilize experimental design and the scientific process to explore new ideas or solve problems.
\item Implement appropriate data collection techniques and analysis to interpret relevant scientific data versus biased data.
\item Evaluate scientific evidence to reach a valid conclusion.
\item Understand and appreciate the interconnectedness of the sciences.
\item Conduct literature reviews in order to incorporate other research into science writings.
\item Present research in front of a group of peers and defend research under questioning.
\item Apply appropriate mathematical principles and graphical analysis to solve problems and support ideas.
\item Utilize statistical tests and methods to accept or fail to accept scientific hypotheses.
\item Use the appropriate lab equipment, techniques, and technology when investigating scientific inquiries.
\item Use models and representations to communicate scientific phenomena and solve scientific problems.
\item Engage in problem solving, inquiry, and design of innovative solutions. 
\item Integrate prior knowledge with new information in novel and creative ways to strengthen overall understanding. 
\item Develop curiosity for the natural world with regard to scientific inquiry.
\item Apply conceptual understanding and critical thinking to real world problems.
\item Promote environmental stewardship.
\item Demonstrate the ability to collaborate with peers during scientific explorations.
\item Make a scientific claim and provide supportive evidence.
\item Connect the microscopic to the macroscopic across scientific disciplines.

\end{itemize}