\section{Portrait of a Graduate}

\textsc{An Indian Springs School graduate, having completed the course of study in Computer Science \& Engineering, will} $\ldots$ 

\begin{itemize}
  \item Learn that solutions to problems, either engineering or programming, are best solved by following a process. While the exact steps can vary from model to model, there is a commonality among all of the procedures. 
  \begin{itemize}
\item Engineering problems are best solved with an iterative design cycle that moves through research, decomposition, modeling, implementation, measuring and testing, communicating results, and back to research.
\item Programming problems are best solved with Computational Thinking that decomposes problems, recognizes patterns, abstracts the rules for those patterns, and then produces algorithms.
\end{itemize}
\item Know how to learn. A graduate will understand the skills and steps needed to learn, discover, and master new information on their own.
\item Be able to seek knowledgeable assistance correctly. A graduate will understand how, when, and where to get assistance from knowledgeable people.
\item Be able to communicate and teach what they know. A graduate will understand how to easily transfer knowledge and skills.
\item Know the four pillars of Object Oriented Programming (OOP); Abstraction, Encapsulation, Inheritance, Polymorphism.
\item Know fundamental programming concepts outside of OOP, such as
\begin{itemize}
\item Data types and data collections; how to access them and what their limitations are.
\item How to make decisions with relational, logical, and control operators. 
\item Big O: a representation of the time and space complexity of algorithms as they scale.
\item Recursion 
\item Top Down Design / Bottom Up Implementation
\end{itemize}
\item Understand how a team efficiently approaches learning about and mastering a topic or area of expertise. A graduate will understand how to manage time and resources for a project.
\item Learn the basic fundamentals of Artificial Intelligence / Neural Networks / Machine Learning
\item Be able to document their work. A graduate will understand the skills and steps needed to create and maintain Engineering, Technical, and Code Repository documentation.
\item Be proficient at managing code in a team software repository and presenting code in a public code repository
\item Be proficient enough with Linux to be more than exceeding comfortable using it in a college environment. A graduate will be conversant enough to accomplish basic programming, data management, and data analysis.

\end{itemize}